Multi-level modeling with Openflexo/\FML

### 2021-09-27 4-technology.tex
Updates from Overleaf
small change to the conclusions

\begin{figure*}
    \centering
    \includegraphics[width=1.0 \textwidth]{Figures/FMLMetaModel.pdf}
    \caption{Internal representation of \FML language}
    \label{fig:mm}
\end{figure*}
%\noteAntoine{Dans la figure ne manque-t-il pas les containements ? (VM vers Concepts)}
%\noteSylvain{C'est le cas dans cette nouvelle figure}

@@

\noteSylvain{Parler plutot ici de représentation interne du language FML (plutot que metamodel qui embrouille le lecteur avec ce qui suit ?}
\FML simplified metamodel is provided in Figure~\ref{fig:mm}. It is designed to define models as virtual models. A virtual model
is composed of a set of \emph{concepts}, while itself being a concept.
Hence, virtual models are structuring units forming architectures while concepts are the
core entities. A concept has a set of \emph{roles} and
\emph{behaviors}. A parallel to object-oriented approach can be useful
to understand \FML\footnote{Some aspects of \FML do not exist in object oriented approach.}. A concept corresponds to a class, its roles to the
attributes of the class and its behaviors to the methods of the class.
These roles have types defining the kind of value the role will point
at runtime.
Whenever a type external to the federation space is used, one needs to use a \emph{model slot}. A model
slot is a mediation entity in charge of giving
access to external elements using
a \emph{technology adapter}\footnote{It is a reusable library that defines
connections between the \FML execution engine and a particular
technological space.}.

@@

Figure \ref{fig:BBPMNSubsetExample} shows...

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=1.0 \textwidth]{Figures/FMLMetaModel.pdf}
    \caption{Representation of the main concepts of \FML language}
    \label{fig:mm}
\end{figure*}
%\noteAntoine{Dans la figure ne manque-t-il pas les containements ? (VM vers Concepts)}
%\noteSylvain{C'est le cas dans cette nouvelle figure}

@@

\FML simplified metamodel is provided in Figure~\ref{fig:mm}. It is designed to define models as virtual models. A virtual model
is composed of a set of \emph{concepts}, while itself being a concept.
Hence, virtual models are structuring units forming architectures while concepts are the
core entities. A concept has a set of \emph{roles} and
\emph{behaviors}. A parallel to object-oriented approach can be useful
to understand \FML\footnote{Some aspects of \FML do not exist in object oriented approach.}. A concept corresponds to a class, its roles to the
attributes of the class and its behaviors to the methods of the class.
These roles have types defining the kind of value the role will point
at runtime.
Whenever a type external to the federation space is used, one needs to use a \emph{model slot}. A model
slot is a mediation entity in charge of giving
access to external elements using
a \emph{technology adapter}\footnote{It is a reusable library that defines
connections between the \FML execution engine and a particular
technological space.}.

\noteSylvain{Retravailler le texte pour parler de tous les concepts qui sont sur la figure}

@@

Figure \ref{fig:BPMNSubsetExample} shows...

\noteSM{We use the current Figure 3 to answer reviewer 1 in the response letter just as to show how the model federation works, but not here.}

\todo{Faire l'explication une fois que l'on aura décidé ce qu'on y montre...}
